---
title: "R Data Cleaning"
author: "Adarsh"
date: "March 15, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## TIDYVERSE
: It is an ecosystem of packages, when imported, imports a group of projects.
  All these packages work together using a 'tidy data format'.
  (More info on https://doi.org/10.21105/joss.01686 )
  
=> "Tidy data is a way of structuring your data to work with the tidyverse,
    in a way of making consistent and robust analysis"

All the packages use 'consistent syntax', 'similar function design' and all 
work 'seemlessly together'.


## Deplyr
: One of the main packages in tidyverse.
  Used for "filtering", "transforming" and "manipulating" the data.
  

```{r}
## Importing tidyverse
library(tidyverse)

## Built in data-set in tidyverse
mpg
```


## Pipe operator 
: When you take one action, you take it's output and then pipe that in as the 
input to another action
%>%
```{r}
## the filter function is going to recieve the entire dataset ('mpg') as the first argument 
mpg %>% 
    dplyr::filter(model=='a4')%>%  # return all rows that satisfy the condition : 'a4' here
    
    dplyr::arrange(displ,cyl)%>% # sort/ reorder your columns : first by displ then by cyl
    
    dplyr::mutate(old <- year<2000,
                  full <- drv=='f')%>% #add new & PRESERVE OLD : maark everything that is older then 2000

    ##  !!! CAUTION SKIP this if you want to keep the old record
#   dplyr::transmute() #add new DROP OLD : 
    
    dplyr::select(-drv) ## keep or remove columns
mpg%>%    
    dplyr::count(model, sort=T) ## Create aggregate stats
```

